Verifying Demonstrations

### 2017-08-11 design.tex
Fixes depth level for TOC in slides
Splits storage into related to privacy, verifiability

@@

We also need to ensure that proofs made by the same person must be linkable 
(\cref{UniqueIndividual}).

@@

>>>>

\begin{frame}
  \begin{question}
    What if Alice acts as a witness for Eve's agents?
    Can that violate her privacy?
  \end{question}
  \begin{question}
    What if Eve's agents act as witnesses?
    Can they track their signatures to track users?
    Can Alice detect if this happens?
  \end{question}
\end{frame}

@@

We also need to ensure that proofs made by the same person must be linkable 
(\cref{CountOnce}).

@@

\subsection{Individual and universal verifiability}

### 2017-08-11 intro.tex

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We thus settle for the following definition.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Organizers want to count anyone who participated \dots
      \item \dots at any time
      \item \dots in any location
    \end{itemize}
  \end{remark}
\end{frame}

\begin{frame}
\begin{definition}[A protest]
  A protest is an event identified by its cause.
\end{definition}
\end{frame}

>>>>

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We thus settle for the following informal definition:
a protest is an event identified by its cause.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Organizers want to count anyone who participated \dots
      \item \dots at any time
      \item \dots in any location
      \item A protest is thus identified by its cause.
    \end{itemize}
  \end{remark}
\end{frame}
